Conditional Generation of Variation and Mean Fitness Increase: \\ Necessity is the Mother of Genetic Invention

### 2017-11-26 ms.tex
revised LS's changes

The \emph{reduction principle} is the widely general phenomenon that, in populations at a balance between natural selection and a process that generates variation (i.e. mutation, migration, or recombination), selection favors neutral modifiers that decrease the rate at which variation is generated. 
The \emph{reduction principle} was demonstrated for modifiers of the recombination~\citep{Feldman1972}, mutation~\citep{Liberman1986a}, migration~\citep{Feldman1986}, and these results were generalized in a unified treatment in a series of studies ~\citep{Altenberg:1984:Book,Altenberg1987,Altenberg:2009:Linear,Altenberg:2012:Resolvent-Positive,Altenberg2012b,Altenberg2017}.

The latter studies establish that that conditions for a \emph{unified reduction principle} for neutral genetic modifiers are:
%are ~\citep{Altenberg:1984:Book,Altenberg1987,Altenberg:2009:Linear,Altenberg2017}:
(i) effectively infinite population size, (ii) constant-viability selection, (iii) a population at an equilibrium, and (iv) \emph{linear variation} -- the equal scaling of transition probabilities by the modifier.
A departure from the latter assumption occurs if two variation-producing processes interact~\citep{Feldman1980,Altenberg2012b}.
Departures from the \emph{reduction principle} have also been demonstrated when conditions (i)-(iii) are not met, see for example~\citet{Holsinger1986} and references therein.

@@

\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms+LA}

>>>>

According to the \emph{reduction principle}, in populations at a balance between natural selection and a process that generates variation (i.e. mutation, migration, or recombination), selection favors neutral modifiers that decrease the rate at which variation is generated. 
The \emph{reduction principle} was demonstrated for modifiers of the recombination~\citep{Feldman1972}, mutation~\citep{Liberman1986a}, and migration~\citep{Feldman1986}.
These results were unified in a series of studies ~\citep{Altenberg1984,Altenberg1987,Altenberg2009,Altenberg2012b,Altenberg2012a,Altenberg2017}.

The latter studies have established the conditions for a \emph{unified reduction principle} by neutral genetic modifiers:
(i) effectively infinite population size, (ii) constant-viability selection, (iii) a population at an equilibrium, and (iv) \emph{linear variation} -- the equal scaling of transition probabilities by the modifier.
A departure from the latter assumption occurs if two variation-producing processes interact~\citep{Feldman1980,Altenberg2012b}.
Departures from the \emph{reduction principle} have also been demonstrated when conditions (i)-(iii) are not met, see for example~\citet{Holsinger1986} and references therein.

@@

\bibliographystyle{agsm}
%\bibliography{/Users/yoavram/Documents/library}
\bibliography{ms}
